\section{Theory}

The effect of any invariant linear system (LTI) on an arbitrary input  signal is
obtained by convolution of the input signal  with  the system's impulse response
function. In a LTI system, the  output  of the system $y(t)$ for an input $x(t)$
can be obtained by the convolution integral:

\begin{equation}
    y(t)=g(t)*x(t)=\int_0^t g(t-\tau)x(\tau)\,d\tau
    \label{eq:conv_int}
\end{equation}

where $g(t)$ is the \textit{impulse response}  of the system. That is, $g(t)$ is
the output of the system with an input $x(t)$ = $\delta(t)$,  where  $\delta(t)$
is the Dirac delta. The impulse response completely  characterizes  the  dynamic
behaviour of the system.

Applying   the   Laplace   transform  to  the  convolution  integral   (equation
\ref{eq:conv_int}) we obtain equation \ref{eq:laplace}:

\begin{equation}
    \laplace[y(t)] = \laplace[g(t) ∗ x(t)] = \laplace[g(t)] \laplace[x(t)]
\end{equation}

or in simple expression:

\begin{equation}
    Y(s) = G(s)X(s)
    \label{eq:laplace}
\end{equation}

where $Y(s)$, $G(s)$ and $X(s)$ are the Laplace transforms of $y(t)$, $g(t)$ and
$x(t)$ respectively. A Transfer Function (TF) is the mathematical representation
of  the  relation between the input and output of a system. In a LTI system,  TF
can be  expressed  as  the  ratio of the Laplace transform of the output and the
input, and  corresponds to the Laplace transform of the impulse response $G(s)$.

\begin{equation}
    G(s) = \frac{Y(s)}{X(s)}
\end{equation}

In order  to  obtain  $G(s)$ from an unknown system, a signal in the form of the
Dirac delta function  must  be applied to the input of the system and its output
must  be  measured.  Unfortunately, it is very hard to do this in most practical
cases, due to:

\begin{enumerate}
    \item Difficulty of generating a Dirac delta function (infinite amplitude, zero time).
    \item Any finite approximation of the Dirac delta function will cause an extremely small and hard to measure response signal.
\end{enumerate}

A far more practical method is to measure the  \textit{step response} instead. A
step function is easier to create in the physical world.  The  derivative of the
resulting measured signal will  very  closely  resemble  its theoretical impulse
response.

\input{sections/theory/model}
\input{sections/theory/characterisation_of_step_responses}
\input{sections/theory/approximating_step_response}
\input{sections/theory/least_squares}

